HSC Synthetic Pipeline I: Basic Design and Characterization of the Photometric Performance of HSC

### 2017-04-10 draft/ms_v1.tex
Draft: small changes in abstract

    The Subaru Strategy Survey Program (SSP) is an ambitious wide-area, multi-band
    survey using the Hyper Suprime-Cam (HSC) on Subaru telescope.
    At the imaging depth of this survey, it becomes challenging to achieve accurate,
    unbiased, and consistent photometry across all five bands.
    In this work, we present \synpipe{}, a \texttt{Python}-based, flexible framework
    that interfaces with the HSC data reduction pipeline (\hscpipe{}) and test its
    performance via injecting synthetic objects to the single-\texttt{visit} HSC images.
    We use the coadd images in two \tracts{} from the Wide layer with representative
    seeing conditions to demonstrate the usage of \synpipe{} and examine the general
    photometric performance of \texttt{hscpipe}.
    We find that the typical uncertainties of HSC \forced{} PSF photometry for stars
    range from ${\sim}0.01$ mag at $i{\sim}18.0$ mag to ${\sim}0.06$ at $i{\sim}25.5$
    mag (1\%-5\% accuracy in the $i$-band).
    For synthetic single-{S\'{e}rsic\ } model galaxies, the typical uncertainties of
    HSC forced \cmodel{} photometry range from 0.14 mag at $i{\sim}20.0$ mag to
    0.20 mag at $i{\sim} 25.2$ mag.
    Over the range of colors and magnitudes in these tests, we find that both \forced{}
    PSF and \cmodel{} photometry provide unbiased estimates of colors that are robust
    against different seeing conditions.
    Finally, we also noticed that 1) the degree that a object is blended with others
    impact the photometric accuracy, especially for stars.
    Highly blended object tends to have larger photometric uncertainty, systematically
    underestimated flux, and slightly biased color.
    2) a relative high fraction of faint stars (${\sim}20$\% at $i>22.5$ mag) could be
    misclassified as extended objects.
    3) the shape and size estimates for galaxies using \cmodel{} suffer from strong
    biases.

>>>>

    The Subaru Strategy Survey Program (SSP) is an ambitious wide-area, multi-band
    survey using the Hyper Suprime-Cam (HSC) on Subaru telescope.
    At the imaging depth of this survey, it becomes challenging to achieve accurate,
    unbiased, and consistent photometry across all five bands.
    In this work, we present \synpipe{}, a \texttt{Python}-based, flexible framework
    that interfaces with the HSC data reduction pipeline (\hscpipe{}) and test its
    performance via injecting synthetic objects to the single-\texttt{visit} HSC images.
    We use coadd images in two \tracts{} from the Wide layer with representative
    seeing conditions to demonstrate the implementation of \synpipe{} and examine the 
    general photometric performance of \texttt{hscpipe}.
    We find that the typical uncertainties of HSC \forced{} PSF photometry for stars
    range from ${\sim}0.01$ mag at $i{\sim}18.0$ mag to ${\sim}0.06$ at $i{\sim}25.5$
    mag (1\%-7\% accuracy in the $i$-band).
    For synthetic galaxies with single-\ser{} model, typical uncertainties of the
    forced \cmodel{} photometry range from 0.14 mag at $i{\sim}20.0$ mag to
    0.20 mag at $i{\sim} 25.2$ mag.
    Over the colors and magnitudes ranges used in these tests, we find that both 
    \forced{} PSF and \cmodel{} photometry provide unbiased estimates of colors that 
    are robust in different seeing conditions.
    Finally, we notice a few issues in the current \hscpipe{} that are worth keeping
    in mind when using HSC data: 
    1) the degree that a object is blended with others impacts the photometric 
    accuracy, especially for point sources.
    Highly blended object tends to have larger photometric uncertainty, systematically
    underestimated flux, and slightly biased color.
    2) a relative high fraction of faint stars (${\sim}16$\% at $i>22.5$ mag) can be
    misclassified as extended objects.
    3) the shape and size estimates for galaxies using \cmodel{} suffer from strong
    biases.
